---
title: "A Longitudinal Analysis of the Synchronized Brainwave Dataset"
author: "Thomas Edwards and Jonathan Skaza"
date: "12/7/2016"
output: beamer_presentation
<<<<<<< HEAD
=======
bibliography: bibliography.bib
>>>>>>> b3ce2ebd748202277cfa9106b63e143c2cb2fb4d
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

## Inspiration
- Has been a growing interest over recent years to further understand the brain's ability to comprehend information at a faster rate
- Researchers at MIT performed an experiment on Monkeys where they discovered that synchronized brain waves enable rapid learning. [@trafton]

```{r fig.height=4, echo=FALSE}
library(png)
library(grid)
img = readPNG("figures/brain.png")
grid.raster(img)
```

## Introduction
- As a next step, we thought it would be intriguing to explore this idea further by investigating how ones' brain waves can be manipulated to maintain a synchronized neurological state so that cognitive function is optimized. 
- To do this we analyzed EEG data collected on subjects exposed to different stimuli.

```{r fig.height=4, echo=FALSE}
library(png)
library(grid)
img = readPNG("figures/device.png")
grid.raster(img)
```

## Background
- Study involved 30 voluntary students from UC Berkeley.
- Participants where randomly assigned to watch one of the two stimulus videos (both videos where 5 minutes and 19 seconds long).
- Everyone was hooked up to an Electroencephalography (EEG) which recorded electrical brain activity as they viewed the video and followed the instructions. 


## Smoothed Trajectories by Subject

```{r traj, echo = FALSE, warning=FALSE, message=FALSE}
ggplot(eeg_clean, aes(indra_time)) + 
  stat_smooth(aes(y=attention_esense)) + 
  stat_smooth(aes(y=meditation_esense), colour="black") +
  facet_wrap(~ id) + xlab("Time") + ylab("Standardized Score") + ylim(c(0,100))
```

<<<<<<< HEAD
## Model

$$
\left(\begin{array}{c}
\mathbf{Y_{1i}} \\
\mathbf{Y_{2i}}
\end{array}\right)
= \mathbf{X_i}^T 
\left(\begin{array}{c}
\boldsymbol{\beta_{1i}} \\
\boldsymbol{\beta_{2i}}
\end{array}\right)
+
\mathbf{Z_i}^T 
\left(\begin{array}{c}
\boldsymbol{b_{1i}} \\
\boldsymbol{b_{2i}}
\end{array}\right)
+
\left(\begin{array}{c}
\boldsymbol{\epsilon_{1i}} \\
\boldsymbol{\epsilon_{2i}}
\end{array}\right)
$$

- \textit{Fixed Effects}: Intercept, Session, Gender, Color, Time, Hidden Icons, Previous Exposure to Ad
- \textit{Random Effects}: Intercept, Time
=======
## References
>>>>>>> b3ce2ebd748202277cfa9106b63e143c2cb2fb4d
